\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-30 latex/article_vol2.tex
Donish

\includepdf[pages=2, pagecommand={\section{Appendix B: User-extended cleaning of
  exampleData} \label{sec:appendix2}}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}
\includepdf[pages=3-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
%\hl{Data cleaning with user supplied extensions here}

>>>>

\includepdf[pages=2, pagecommand={\section{Appendix B: User-extended cleaning of
  exampleData} \label{sec:appendix2}}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
\includepdf[pages=3-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
%\hl{Data cleaning with user supplied extensions here}
